---
title: "Linear regression - interaction between treatment and maternal education - gross"
author: "Pearl Ante-Testard"
date: "`r Sys.Date()`"
output: pdf_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, 
                          encoding   = encoding, 
                          output_dir = here::here("output")
                          )})
---


```{r clean environment, echo=FALSE}

rm(list=ls(all=TRUE))

```

```{r packages and functions, echo = TRUE, warning = FALSE}

source(here::here("R", "0-config.R"))

```

```{r read formatted data, echo=TRUE, warning=FALSE}

df_analysis_gross <- readRDS(file = here::here("data", "1-final", "df_analysis_iwi.rds")) %>% 
  dplyr::mutate(study = sub("s[0-9]*_", "", study.x)) %>%
  select(study, pid, region, cluster, arms_maternal, raw_mateducat, d8_grossmotor_el, iwi) %>%
  dplyr::filter(!is.na(raw_mateducat)) %>%
  dplyr::filter(!is.na(arms_maternal)) %>%
  dplyr::filter(!is.na(d8_grossmotor_el)) %>%
  dplyr::mutate(
    arms_maternal = factor(arms_maternal, levels = c(0, 1), labels = c("Control", "SQ-LNS")),
    mateduc_cat = case_when(
      raw_mateducat %in% c(0, 1) ~ "No/incomplete primary",
      raw_mateducat %in% c(2, 3) ~ "Complete primary/inc.secondary",
      raw_mateducat %in% c(4) ~ "Secondary or greater"
    ),
    mateduc_cat = factor(mateduc_cat, levels = c("No/incomplete primary", "Complete primary/inc.secondary", "Secondary or greater")),
    mateduc_num = case_when(
      raw_mateducat == 0 ~ 0,
      raw_mateducat == 1 ~ 1,
      raw_mateducat %in% c(2, 3, 4) ~ 2
    ),
    mateduc_num = as.numeric(mateduc_num),
    iwi = as.numeric(iwi),
    cluster = factor(cluster),
    region = factor(region),
    study = factor(study)
  )

# Print the first few rows of the dataframe to verify
head(df_analysis_gross)

table(df_analysis_gross$study, df_analysis_gross$mateduc_cat)
        
```

# Fit linear regression with the interaction term between arms_maternal and IWI.

## Here, we used lm_robust() to be able to account for clustering in the data when applicable.

```{r interaction results, echo=TRUE, warning=FALSE}

# Fit the simpler model without interaction
model_noint <- lm_robust(d8_grossmotor_el ~ mateduc_cat + arms_maternal, data = df_analysis_gross,
                         clusters = study)

# Fit the more complex model with interaction
model_int <- lm_robust(d8_grossmotor_el ~ mateduc_cat + arms_maternal + mateduc_cat * arms_maternal, data = df_analysis_gross, clusters = study)

# Perform the Wald test
waldtest_result <- waldtest(model_int, model_noint)

# Print the result
print(waldtest_result)

```


```{r interaction results, echo=TRUE, warning=FALSE}

inter <- df_analysis_gross %>%
  split(.$study) %>%
  map_dfr(function(df_analysis_gross) {
    study_name <- unique(df_analysis_gross$study)
    results <- list()
    
    if (study_name %in% c("DOSE", "GHANA", "HAITI", "DYADG", "DYADM")) {
      model <- lm_robust(d8_grossmotor_el ~ mateduc_cat + arms_maternal + 
                           mateduc_cat * arms_maternal, 
                         data = df_analysis_gross)
      
      beta_interaction_treat_primary_incSecondary <- coef(model)["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS"]
      model_summary <- summary(model)
      ci_lower_primary_incSecondary <- model_summary$coefficients["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS", "CI Lower"]
      ci_upper_primary_incSecondary <- model_summary$coefficients["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS", "CI Upper"]
      se_primary_incSecondary <- model_summary$coefficients["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS", "Std. Error"]
      
      beta_interaction_treat_secondary_greater <- coef(model)["mateduc_catSecondary or greater:arms_maternalSQ-LNS"]
      model_summary <- summary(model)
      ci_lower_secondary_greater <- model_summary$coefficients["mateduc_catSecondary or greater:arms_maternalSQ-LNS", "CI Lower"]
      ci_upper_secondary_greater <- model_summary$coefficients["mateduc_catSecondary or greater:arms_maternalSQ-LNS", "CI Upper"]
      se_secondary_greater <- model_summary$coefficients["mateduc_catSecondary or greater:arms_maternalSQ-LNS", "Std. Error"]
      
      results$intervention <- list(inter_treat_primary_incSecondary = beta_interaction_treat_primary_incSecondary, 
                                   ci_low_primary_incSecondary = ci_lower_primary_incSecondary, 
                                   ci_up_primary_incSecondary = ci_upper_primary_incSecondary, 
                                   se_primary_incSecondary = se_primary_incSecondary,
                                   inter_treat_secondary_greater = 
                                     beta_interaction_treat_secondary_greater, 
                                   ci_low_secondary_greater = ci_lower_secondary_greater, 
                                   ci_up_secondary_greater = ci_upper_secondary_greater, 
                                   se_secondary_greater = se_secondary_greater
                                   )
      
    } else {
      model <- lm_robust(d8_grossmotor_el ~ mateduc_cat + arms_maternal + mateduc_cat * arms_maternal, 
                         data = df_analysis_gross, clusters = cluster)
      
    beta_interaction_treat_primary_incSecondary <- coef(model)["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS"]
      model_summary <- summary(model)
      ci_lower_primary_incSecondary <- model_summary$coefficients["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS", "CI Lower"]
      ci_upper_primary_incSecondary <- model_summary$coefficients["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS", "CI Upper"]
      se_primary_incSecondary <- model_summary$coefficients["mateduc_catComplete primary/inc.secondary:arms_maternalSQ-LNS", "Std. Error"]
      
      beta_interaction_treat_secondary_greater <- coef(model)["mateduc_catSecondary or greater:arms_maternalSQ-LNS"]
      model_summary <- summary(model)
      ci_lower_secondary_greater <- model_summary$coefficients["mateduc_catSecondary or greater:arms_maternalSQ-LNS", "CI Lower"]
      ci_upper_secondary_greater <- model_summary$coefficients["mateduc_catSecondary or greater:arms_maternalSQ-LNS", "CI Upper"]
      se_secondary_greater <- model_summary$coefficients["mateduc_catSecondary or greater:arms_maternalSQ-LNS", "Std. Error"]
      
      results$intervention <- list(inter_treat_primary_incSecondary = beta_interaction_treat_primary_incSecondary, 
                                   ci_low_primary_incSecondary = ci_lower_primary_incSecondary, 
                                   ci_up_primary_incSecondary = ci_upper_primary_incSecondary, 
                                   se_primary_incSecondary = se_primary_incSecondary,
                                   inter_treat_secondary_greater = 
                                     beta_interaction_treat_secondary_greater, 
                                   ci_low_secondary_greater = ci_lower_secondary_greater, 
                                   ci_up_secondary_greater = ci_upper_secondary_greater, 
                                   se_secondary_greater = se_secondary_greater
                                   )
      
    }
    
    # Create a data frame with the results
    inter_tab <- data.frame(
      study = study_name,
      inter_treat_primary_incSecondary = round(results$intervention$inter_treat_primary_incSecondary, 3),
      ci_low_primary_incSecondary = round(results$intervention$ci_low_primary_incSecondary, 3),
      ci_up_primary_incSecondary = round(results$intervention$ci_up_primary_incSecondary, 3),
      se_primary_incSecondaryy = round(results$intervention$se_primary_incSecondary, 3),
      inter_treat_secondary_greater = round(results$intervention$inter_treat_secondary_greater, 3),
      ci_low_secondary_greater = round(results$intervention$ci_low_secondary_greater, 3),
      ci_up_secondary_greater = round(results$intervention$ci_up_secondary_greater, 3),
      se_secondary_greater = round(results$intervention$se_secondary_greater, 3)
    )
    
    return(inter_tab)
  })

print(inter)

```

# Meta-analysis of the slopes (arms_maternalSQ-LNS:maternal education) and their standard errors/confidence intervals from the original linear regression models

## Using the slope/coefficients from the interaction term and standard error from the model (maternal education:arms_maternalSQ-LNS), we performed a random-effect meta-analysis to get the pooled slope and standard error.

```{r meta, echo=TRUE, warning=FALSE}

# Define the tau.method
tau.method <- "REML"

meta1_primary_incSecondary <- metagen(
    TE = inter$inter_treat_primary_incSecondary,
    seTE = inter$se_primary_incSecondary,
    lower = inter$ci_low_primary_incSecondary,
    upper = inter$ci_up_primary_incSecondary,
    method.tau = tau.method,
    hakn = FALSE,
    studlab = inter$study
  )

forest_meta_primary_incSecondary <- forest(meta1_primary_incSecondary, 
       layout = "JAMA", 
       leftlabs = c("Study", "d8_grossmotor_el (primary/inc.Secondary:arms_maternalSQ-LNS) [95% CI]"),
       label.right = "Favorable", 
       label.left = "Unfavorable",
       digits = 3,
       prediction.subgroup = inter$arms_maternal)
forest_meta_primary_incSecondary


meta1_secondary_greater <- metagen(
    TE = inter$inter_treat_secondary_greater,
    seTE = inter$se_secondary_greater,
    lower = inter$ci_low_secondary_greater,
    upper = inter$ci_up_secondary_greater,
    method.tau = tau.method,
    hakn = FALSE,
    studlab = inter$study
  )

forest_meta_secondary_greater <- forest(meta1_secondary_greater, 
       layout = "JAMA", 
       leftlabs = c("Study", "d8_grossmotor_el (secondary/greater:arms_maternalSQ-LNS) [95% CI]"),
       label.right = "Favorable", 
       label.left = "Unfavorable",
       digits = 3,
       prediction.subgroup = inter$arms_maternal)
forest_meta_secondary_greater
```


# Session info
```{r session info}

sessionInfo()
```
