---
title: "Descriptive statistics of baseline growth outcomes"
author: "Pearl Ante-Testard"
data: "`r Sys.Date()`"
output: html_document
knit: (function(inputFile, encoding){s
    rmarkdown::render(inputFile,
                      encoding = encoding,
                      output_dir = here::here("output"))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r configuration, echo = FALSE, message = FALSE}

library(here)
library(tidyverse)
library(table1)
```

```{r load data, echo = FALSE}

df_analysis <- readRDS(here::here("data", "1-final",
                                  "IPD_full_20200905_growth_formatted.RDS")) %>%
  filter(!is.na(arm_primary)) %>%
  filter(!is.na(sesindex))
```

```{r wealth tertile, echo = FALSE}

df_analysis <- df_analysis %>%
  group_by(study) %>%
  mutate(sesindex_ter = ntile(sesindex, 3)) %>%
  ungroup()
```

```{r render function, echo = FALSE}

rndr <- function(x, name, ...) {
  if (!is.numeric(x)) return(render.categorical.default(x))
  what <- switch(name,
                 laz_bl = "Mean (SD)",
                 wlz_bl = "Mean (SD)",
                 matht = "Mean (SD)",
                 matwt = "Mean (SD)",
                 matage = "Mean (SD)",
                 sesindex = "Median (IQR)")
  parse.abbrev.render.code(c("", what))(x)
}
```

```{r render baseline characteristics, echo = FALSE}

tab1 <- df_analysis %>%
  mutate(severe_stunted_bl = fct_drop(factor(severe_stunted_bl), only = "0"),
         `Severe stunting` = factor(case_when(severe_stunted_bl == 1 ~ "Yes")),
         severe_wasted_bl = fct_drop(factor(severe_wasted_bl), only = "0"),
         `Severe wasting` = factor(case_when(severe_wasted_bl == 1 ~ "Yes")),
         `Wealth tertiles` = factor(sesindex_ter, labels = c("T1", "T2", "T3")),
         tx_table1 = factor(arm_primary, labels = c("Control", "SQ-LNS"))) %>%
  labelled::set_variable_labels(sesindex = "Wealth index",
                                laz_bl = "Mean LAZ",
                                wlz_bl = "Mean WLZ",
                                matht = "Maternal height",
                                matwt = "Maternal weight",
                                matage = "Maternal age") %>%
  # render
  table1(~ sesindex + `Wealth tertiles` + laz_bl + wlz_bl + `Severe stunting` + `Severe wasting` + # nolint
           matht + matwt + matage
        | study*tx_table1, data = .,overall = F, rowlabelhead = "Baseline characteristics between arms", # nolint
          render = rndr, topclass="Rtable1") # nolint

tab1
```

```{r render baseline characteristics by wealth, echo = FALSE}

tab2 <- df_analysis %>%
  mutate(severe_stunted_bl = fct_drop(factor(severe_stunted_bl), only = "0"),
         `Severe stunting` = factor(case_when(severe_stunted_bl == 1 ~ "Yes")),
         severe_wasted_bl = fct_drop(factor(severe_wasted_bl), only = "0"),
         `Severe wasting` = factor(case_when(severe_wasted_bl == 1 ~ "Yes")),
         sesindex_ter = factor(sesindex_ter, labels = c("T1", "T2", "T3")), # nolint
         tx_table1 = factor(arm_primary, labels = c("Control", "SQ-LNS")),
         study = factor(study)) %>% # nolint
  labelled::set_variable_labels(sesindex = "Wealth index",
                                laz_bl = "Mean LAZ",
                                wlz_bl = "Mean WLZ",
                                matht = "Maternal height",
                                matwt = "Maternal weight",
                                matage = "Maternal age") %>%
  # render
  table1(~ laz_bl + wlz_bl + `Severe stunting` + `Severe wasting` +
           matht + matwt + matage
        |study*sesindex_ter, data = .,overall = F, rowlabelhead = "Baseline characteristics by wealth quintiles", # nolint
          render = rndr, topclass="Rtable1") # nolint

tab2
```

tab3 <- df_analysis %>%
  mutate(severe_stunted_bl = fct_drop(factor(severe_stunted_bl), only = "0"),
         `Severe stunting` = factor(case_when(severe_stunted_bl == 1 ~ "Yes")),
         severe_wasted_bl = fct_drop(factor(severe_wasted_bl), only = "0"),
         `Severe wasting` = factor(case_when(severe_wasted_bl == 1 ~ "Yes")),
         sesindex_ter = factor(sesindex_ter, labels = c("T1", "T2", "T3")), # nolint
         tx_table1 = factor(arm_primary, labels = c("Control", "SQ-LNS")),
         study = factor(study)) %>% # nolint
  labelled::set_variable_labels(sesindex = "Wealth index",
                                laz_bl = "Mean LAZ",
                                wlz_bl = "Mean WLZ",
                                matht = "Maternal height",
                                matwt = "Maternal weight",
                                matage = "Maternal age") %>%
  # render
  table1(~ laz_bl + wlz_bl + `Severe stunting` + `Severe wasting` +
           matht + matwt + matage
        |study*tx_table1*sesindex_ter, data = .,overall = F, rowlabelhead = "Baseline characteristics by wealth quintiles", # nolint
          render = rndr, topclass="Rtable1") # nolint

tab3
```

```{r session info}

sessionInfo()
```